\tool: Automated Generation of Diversified Tests for Self-driving Cars from Existing Maps

### 2021-08-20 paper/main.tex
WIP on section 4

\subsection{Generating Relevant Scenarios}
Legal trajectories across intersections such as the ones reported in Figure~\ref{fig:samples-cubetown} define relevant driving scenarios. Legal trajectories follow the traffic directions encoded into the lanelets. Additionally, we limit \tool to consider the simplest form of legal trajectory, i.e., those that do not require the ego-vehicle to change lanes to pass the intersections. Therefore, one typical generated driving scenario will start on a given lane \emph{before} entering an intersection, continue on the same lane across the intersection, and end on the (logically) same lane \emph{after} the intersection.
%
\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{images/lanelet01}
  \caption{An example of parts of intersection constructed by Salvo. (1) Starting on a given lane, (2) Entering an intersection, (3) Continue on the same lane.}
  \label{fig:intersection_sf}
\end{figure}

\tool generates driving scenarios by selecting the lanelets that belong to an intersection (Figure~\ref{fig:intersection_sf}) and then including those lanelets outside the intersection that \emph{precede} and \emph{follow} the selected ones. Notably, because intersections have various configurations (e.g., number of entering and exiting lanes), the generated driving scenarios indeed force the ego-vehicle to turn left, turn right, or go straight through the intersection.

The generated scenarios are composed of the smallest number (i.e., three) of lanelets. This feature arguably increases the understandability of the resulting test cases but does not necessarily guarantee fast test executions. The lanelets that precede and follow an intersection might be extensive; hence, it may require some time to be fully traversed. Therefore, to reduce execution time, \tool places the ego-vehicle at a fixed distance before entering the intersection and sets the target position to reach at a fixed distance after passing the intersection. Because those distances are configurable, testers can control the duration of test executions and make them more predictable.

\subsection{Selecting Diversified Scenarios}
Up to this point, \tool has not considered the diversity of scenarios. It simply generates as many scenarios as possible to explore the possibilities offered by the input road map. However, many trajectories may stress the ego-vehicle similarly, for example, by forcing it to drive straight through the same intersections from multiple directions. Therefore, \tool filters out test cases that are too similar to each other; hence, improving testing cost-efficiency.

This paper studies two (greedy) approaches for filtering out similar test cases based on distance and feature maps.

@@

\subsection{Spicing Up the Test Cases}
The tests generated by \tool are plain: they stress the ability of the ego-vehicle to plan trajectories that pass intersections and keep the lane but involve no other element besides the ego-vehicle and possibly traffic lights. 
Therefore, we illustrate how those test cases can be extended by placing static obstacles on the course of the ego-vehicle by letting  \tool place parked vehicles on the roads.

>>>>

\subsection{Generating Relevant Scenarios}
\tool generates abstract driving scenarios that follow legal trajectories across intersections such as those reported in Figure~\ref{fig:samples-cubetown}. We define those trajectories as legal because they follow the traffic directions encoded into the lanelets. Additionally, we limit \tool to consider only the simplest form of such trajectories, i.e., those that do not require the ego-vehicle to switch lanes. Therefore, a typical driving scenario generated by \tool starts on a lane \emph{before} an intersection, continues on the same lane across that intersection, and finally ends on the (logically) same lane \emph{after} that intersection.
%
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{images/lanelet01}
 \caption{An example of an abstract driving scenario generated by \tool in the Cube Town map. The scenario  starts on a lane~(1), continues inside the intersection by following the lane~(2), and ends on the same lane after passing the intersection (3).}
 \label{fig:intersection_sf}
\end{figure}

\tool generates driving scenarios by selecting the lanelets that belong to an intersection (Figure~\ref{fig:intersection_sf}) and then including those lanelets outside the intersection that precede and follow the selected ones. Notably, because intersections have various configurations (e.g., number of entering and exiting lanes), the generated driving scenarios can stress different behaviors of ego-vehicle by forcing it to turn left, turn right, or go straight through the intersection.

The generated scenarios are composed of the smallest number (i.e., three) of lanelets. This feature arguably increases the understandability of the resulting test cases but does not necessarily guarantee fast test executions. For example, the lanelets preceding or following an intersection may be long, requiring some time to be fully traversed during test execution. Therefore, to reduce execution time, \tool places the ego-vehicle at a fixed distance before entering the intersection and sets the target position to reach at a fixed distance after passing the intersection. Because those distances are configurable, testers can control the duration of test executions and enable the generation of tests involving obstacles (see~Section~\ref{sec:spicing-up}).

\subsection{Selecting Diversified Scenarios}
Up to this point, \tool does not take the diversity of scenarios into account as it simply generates as many scenarios as possible to explore the possibilities offered by the input road map. However, many legal trajectories may stress the ego-vehicle similarly; for example, they may force it to drive straight through the same intersections from multiple directions. Therefore, \tool filters out test cases that are too similar to each other to improve testing cost-efficiency.

We experimented with two (greedy) approaches for filtering out similar test cases based on distance metrics and feature maps.

@@

\subsection{Spicing Up the Test Cases}
\label{sec:spicing-up}
The tests generated by \tool are plain: they stress the ability of the ego-vehicle to plan trajectories that pass intersections and keep the lane but involve no other element besides the ego-vehicle and possibly traffic lights. 
Therefore, we illustrate how those test cases can be extended by placing static obstacles on the course of the ego-vehicle by letting  \tool place parked vehicles on the roads.
